---
title: "Work Life Talents"
author: "WLT-AI-Bot & Chief Economist"
date:  "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    #theme: null
    self_contained: true
    css: styles.css
---

[Youtube: Work Life Talents](https://www.youtube.com/@Work-Life-Talents) / [Spotify: Work Life Talents](https://open.spotify.com/show/2pAXFkisgq1rC5L0EjHLOI?si=7e4e2af10ab44eab) / [Apple: Work Life Talents](https://podcasts.apple.com/ch/podcast/work-life-talents/id1760824381)

```{r, echo=FALSE}
#htmltools::img(src = knitr::image_uri(paste(getwd(),"/WLT.jpg",sep="")), 
#               alt = 'logo', 
#               style = 'position:absolute; top:0; right:300px; padding:10px;',
#               width = "150px",
#               heigth = "150px")
```


```{r , include=FALSE, echo = FALSE}
## Library
library(tidyverse)
library(tidyquant)
library(timetk)

# scraping data from Yahoo
library(stringr)

# nice tables
library(DT)


library(plotly)

# to get data with python
library(reticulate)

library(readxl)

library(htmltools)

source("../../shinyApp/functions/summary_ret_sd_table.R")
```

```{r , include=FALSE,  echo=FALSE}
## Functions
scrapData = function(ticker, sector = FALSE, title = FALSE){
  print(ticker)
  sec = tit = NA
  
  url = paste("https://in.finance.yahoo.com/quote/", ticker, "/profile", sep = "")
  mydata = as.data.frame(readLines(url, warn = FALSE))
  names(mydata) = "text"
  # sector
  if (sector){
    sec = str_match(as.character(mydata[24, ]),'Sector(.{50})')[, 2]
    sec = substr(sec,regexpr('">',sec)[1]+2,nchar(sec)-6)
  }
  
  # name
  if (title){
    tit = str_match(as.character(mydata[1, ]),'title(.{60})')[, 2]
    tit = substr(tit,2,regexpr("Company",tit)[1]-2)
  }
  
  tickerInfo = c(tit, sec)
  
  return(tickerInfo)
}


scrapDesc = function(ticker){
  print(ticker)
  
  description = NA
  
  url = paste("https://finance.yahoo.com/quote/", ticker, "/profile", sep = "")
  mydata = as.data.frame(readLines(url))
  names(mydata) = "text"
  
  description = str_match(as.character(mydata[24, ]),'Description(.{2000})')[,2]
  
  if(is.na(description)){
    description = NA
  } else{
    
    if (regexpr('">',description)[1]>0){
      tmpStart = regexpr('">',description)[1]
    } else {
      print("something wrong here")
    }
    
    if (regexpr("</p>",description)[1]<0){
      tmpEnd = 2000
    } else {
      tmpEnd = regexpr("</p>",description)
    }
    
    description = substr(description, tmpStart+2, tmpEnd-1)
  }
  return(description)
}

# tmp <- as.character(mydata[5, ])
# save(tmp, file=".txt", ascii = TRUE)

```


```{r , echo = FALSE}
## Ticker

### Portfolio Ticker
end.date = as.Date(Sys.Date(), format('%d/%m/%Y')) 
reportingDate <-  if(weekdays(end.date-1) == "Sonntag") {
  end.date - 3
} else if (weekdays(end.date-1) == "Samstag"){
  end.date-2
} else{ 
  end.date-1}

watchlist <- read_xlsx(paste(getwd(),"/WLT-Titelliste.xlsx", sep=""), sheet = "Aktien", .name_repair = "unique_quiet")
sektoren <- read_xlsx(paste(getwd(),"/WLT-Titelliste.xlsx", sep=""), sheet = "Sektoren", .name_repair = "unique_quiet")
portfolio <-  read_xlsx(paste(getwd(),"/WLT-Titelliste.xlsx", sep=""), sheet = "Portfolio", .name_repair = "unique_quiet")
etf_ch <- read_xlsx(paste(getwd(),"/WLT-Titelliste.xlsx", sep=""), sheet = "ETF-CH", .name_repair = "unique_quiet")

```


```{r , echo = FALSE}
### Benchmark Ticker
#sectors <- c("XLE","XLK","XLC","XLRE","XLU","XLF","XLY","XLP","XLV","XLI","XLB")
```

```{r , echo = FALSE}
## Story
#descInfo <- mapply(scrapDesc, ptf.stk)
#descInfo


```


```{r , include=FALSE, echo = FALSE}
### Yahoo Data with R

#* Get data ----
stk_tbl <- watchlist$Ticker %>%
  tq_get(get  = "stock.prices",
         from = "2019-06-01" ,
         to   = end.date) %>%
  group_by(symbol) 


sector_tbl <- sektoren$Ticker %>%
  tq_get(get  = "stock.prices",
         from = end.date-360 ,
         to   = end.date) %>%
  group_by(symbol)


ptf_tbl <- portfolio$Ticker %>%
  tq_get(get  = "stock.prices",
         from = "2019-06-01" ,
         to   = end.date) %>%
  group_by(symbol) 

etf_ch_tbl <- etf_ch$Ticker %>%
  tq_get(get  = "stock.prices",
         from = "2015-01-01" ,
         to   = end.date) %>%
  group_by(symbol)

# Scrap ticker info data from Yahoo
#ptf.info <- mapply(scrapData, ptf.stk, sector = TRUE, title = TRUE)
#tmpPtfInfo  <- as.data.frame( cbind(ptf.stk, t(ptf.info) ) )
#colnames(tmpPtfInfo) <- c("symbol" ,"name", "sector")

# last price
last <- select( filter(stk_tbl, date == reportingDate), "symbol", "adjusted", "date") %>%
  mutate(adjusted = round(adjusted,2))

colnames(last) <- c("Ticker", "adjusted", "date")

ptfInfo <- left_join( watchlist,  last, by = "Ticker") 



#secInfo <- mapply(scrapData, sectors, sector = FALSE, title = TRUE)
#secInfo <- secInfo[1, ]

```
## Übersicht {.tabset}
### Diskutierte Aktien
<!--
```{r echo=FALSE, warning=FALSE}

l <- htmltools::tagList()

for (iSymbol in watchlist$Ticker){
  
  tmp <- select( filter(stk_tbl, symbol == iSymbol), "symbol", "adjusted", "date")
  tmpinfo <- select(filter(watchlist, Ticker == iSymbol), "Preis", "Diskussionsdatum", "Wunschkurs")
  # hard stopp loss
  #tmpinfo <- tmpinfo %>%
  #  mutate(SL = Preis*0.8)
  
  # trailing stopp-loss
  #tmp2 <- tmp %>%  filter_by_time(.date_var = date, .start_date = watchlist$Diskussionsdatum, .end_date = "end") %>% 
  #  slice(which.max(adjusted)) %>%
  #  mutate(tSL = adjusted*0.8)
  
  
  p <- plot_ly(tmp,x = ~date, y = ~adjusted, type = 'scatter', mode = 'lines', name = ~symbol )
  p <-  add_trace(p, data = tmpinfo,  x = ~Diskussionsdatum, y = ~Preis,  type = "scatter", mode='markers', name = "Diskutiert") # bought
  #p <-  add_lines(p, data = tmp, x = ~date, y = tmpinfo$SL, name = "Stopp-Loss") # SL
  #p <-  add_lines(p, data = tmp, x = ~date, y = tmp2$tSL, name = "traiing Stopp-Loss") # trailing SL
  p <- add_lines(p, data = tmp, x = ~date, y = tmpinfo$Wunschkurs, name = "Wunschkurs")
  p<- add_ribbons(p, data= tmp, x=~date, ymin= 0.95*tmpinfo$Wunschkurs, ymax=1.05*tmpinfo$Wunschkurs, name="5% Band", line=list(opacity=0.3, width=0))
  
  l[[iSymbol]] <- p

}

#%>% add_markers(x = ~date, y = ~adjusted)

l


```
-->




```{r echo=FALSE,  out.width="100%", message=FALSE, warning=FALSE}

# Last price
last <- stk_tbl %>%
  filter(date == reportingDate) %>%
  select(symbol, adjusted, date) %>%
  mutate(adjusted = round(adjusted, 2))

colnames(last) <- c("Ticker", "adjusted", "date")

ptfInfo <- left_join(watchlist, last, by = "Ticker")

# Prepare the combined data
combined_data <- stk_tbl %>%
  inner_join(watchlist, by = c("symbol" = "Ticker"))


create_traces <- function(data) {
  ticker <- data$symbol[1]
  Preis_trace <- list(
    x = data$Diskussionsdatum,
    y = data$Preis,
    type = 'scatter',
    mode = 'markers',
    marker = list(color = 'red', size = 6),
    name = paste(ticker, "Preis"),
    visible = FALSE
  )
  
   main_trace <- list(
    x = data$date,
    y = data$close,
    type = 'scatter',
    mode = 'lines',
    name = ticker,
    line = list(color = "#003172"),
    visible = FALSE
  )
   
  WK_trace <- list(
    x = data$date,
    y = data$Wunschkurs,
    type = 'scatter',
    mode = 'lines',
    name = "Wunschkurs",
    line = list(color = "#B3D4FF"),
    visible = FALSE
  )
  
  list(
    main_trace,
    Preis_trace,
    WK_trace
  )
}

# Apply the function to each ticker's data
traces_list <- combined_data %>%
  group_split(symbol) %>% 
  lapply(create_traces)

# Flatten the list of traces
traces <- do.call(c, traces_list)

fig <- plot_ly()

for (trace in traces) {
  fig <- add_trace(fig, x = trace$x, y = trace$y, type = trace$type, mode = trace$mode, name = trace$name, line = trace$line, marker = trace$marker, visible = trace$visible)
}

# Initially display the first ticker's data
fig <- fig %>%
  layout(
    title = "Aktien im Fokus",
    updatemenus = list(
      list(
        buttons = lapply(seq_along(watchlist$Ticker), function(i) {
          visibility <- rep(FALSE, length(traces))
          visibility[(3 * (i - 1) + 1):(3 * i)] <- TRUE
          list(
            method = "restyle",
            args = list("visible", visibility),
            label = sort(watchlist$Ticker)[i]
          )
        }),
        direction = "down",
        pad = list('r' = 0, 't' = 10),
        showactive = TRUE,
        x = 1.4,
        xanchor = 'right',
        y = 1.1,
        yanchor = 'bottom'
      )
    )
  )

# Set the visibility of the first ticker's traces to TRUE
for (i in 2:4) {
 fig$x$attrs[[i]]$visible <- TRUE
}

fig

```


Youtube / Spotify Übersicht
```{r , echo=FALSE}

#ptfData <- left_join(ptf.data, ptfInfo, by = c("symbol"))

datatable(ptfInfo,
          options = list(
            columnDefs = list(
              list(targets = 6, render = JS("function(data, type, row, meta) {
                                            return '<a href=\"' + data + '\" target=\"_blank\">'+data+'</a>';
                                            }")
            )
          )
        )
)

```

Renditen
```{r , echo=FALSE, warning=FALSE}


#############################
# calculate returns & standard deviation
#############################
stk_summary <- summary_ret_sd_table(stk_tbl)
datatable(as.data.frame(stk_summary))
```

### Aktien Indizes

Hier kommt bald eine Übersicht zu unserer Rubrik Aktien Indizes


### WLT Portfolio
```{r echo=FALSE, message=FALSE, warning=FALSE}

# # Last price
# last <- ptf_tbl %>%
#   filter(date == reportingDate) %>%
#   select(symbol, adjusted, date) %>%
#   mutate(adjusted = round(adjusted, 2))
# 
# colnames(last) <- c("Ticker", "adjusted", "date")
# 
# ptfInfo <- left_join(portfolio, last, by = "Ticker")
# 
# # Prepare the combined data
# combined_data <- ptf_tbl %>%
#   inner_join(portfolio, by = c("symbol" = "Ticker"))
# 
# 
# create_traces <- function(data) {
#   ticker <- data$symbol[1]
#   Preis_trace <- list(
#     x = data$Diskussionsdatum,
#     y = data$Preis,
#     type = 'scatter',
#     mode = 'markers',
#     marker = list(color = 'red', size = 6),
#     name = paste(ticker, "Preis"),
#     visible = FALSE
#   )
#   
#    main_trace <- list(
#     x = data$date,
#     y = data$close,
#     type = 'scatter',
#     mode = 'lines',
#     name = ticker,
#     line = list(color = "#003172"),
#     visible = FALSE
#   )
#    
#   
#   list(
#     main_trace,
#     Preis_trace
#   )
# }
# 
# # Apply the function to each ticker's data
# traces_list <- combined_data %>%
#   group_split(symbol) %>% 
#   lapply(create_traces)
# 
# # Flatten the list of traces
# traces <- do.call(c, traces_list)
# 
# fig <- plot_ly()
# 
# for (trace in traces) {
#   fig <- add_trace(fig, x = trace$x, y = trace$y, type = trace$type, mode = trace$mode, name = trace$name, line = trace$line, marker = trace$marker, visible = trace$visible)
# }
# 
# # Initially display the first ticker's data
# fig <- fig %>%
#   layout(
#     title = "WLT Portfolio Fokus",
#     updatemenus = list(
#       list(
#         buttons = lapply(seq_along(portfolio$Ticker), function(i) {
#           visibility <- rep(FALSE, length(traces))
#           visibility[(2 * (i - 1) + 1):(2 * i)] <- TRUE
#           list(
#             method = "restyle",
#             args = list("visible", visibility),
#             label = sort(portfolio$Ticker)[i]
#           )
#         }),
#         direction = "down",
#         pad = list('r' = 0, 't' = 10),
#         showactive = TRUE,
#         x = 1.4,
#         xanchor = 'right',
#         y = 1.1,
#         yanchor = 'bottom'
#       )
#     )
#   )
# 
# # Set the visibility of the first ticker's traces to TRUE
# for (i in 2:3) {
#  fig$x$attrs[[i]]$visible <- TRUE
# }
# 
# fig

```

```{r, echo=FALSE, warning=FALSE}
# Portfolio Gewichtungen


# fig <- plot_ly(portfolio, labels = ~Name, values = ~Anteil, type = 'pie')
# fig <- fig %>% layout(title = 'Initiale Gewichtung',
#                       xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
#                       yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
# 
# fig
```

### Sektor Aktien
```{r, echo=FALSE, warning=FALSE}


#############################
# calculate returns & standard deviation
#############################
sector_summary <- summary_ret_sd_table(sector_tbl)
datatable(as.data.frame(sector_summary))
```


### ETF Übersicht
Schweizer ETF
```{r, echo=FALSE, warning=FALSE}
### Risk-Return Sectors

#############################
# calculate returns & standard deviation
#############################
etf_ch_summary <- summary_ret_sd_table(etf_ch_tbl)
datatable(as.data.frame(etf_ch_summary))
```


## Disclaimer
<small>     
Data is from Yahoo Finance. DO YOUR OWN RESEARCH !!! WE ARE NOT RESPONSIBLE FOR YOUR PERSONAL LOSSES! 

This is not a personal recommendation, nor an offer to buy or sell nor a solicitation to buy or sell any securities, investment products or other financial instruments or services. This material is distributed for general informational and educational purposes only and is not intended to constitute legal, tax, accounting or investment advice. The statements in this document shall not be considered as an objective or independent explanation of the matters. Please note that this document (a) has not been prepared in accordance with legal requirements designed to promote the independence of investment research, and (b) is not subject to any prohibition on dealing ahead of the dissemination or publication of investment research. “Publications” do not reflect any opinions of the Work-Life-Talents members. Publications are meant for informational purposes only, are not intended to serve as a recommendation to by or sell any security in a brokerage account or any platform, and are not an offer or sale of a security nor an endorsement or advertisement of the same. While the Work-Life-Talent members seek to ensure the accuracy of the information it presents, it has no obligation and shall not be liable for errors in any data, information, or Publications accessible through the Work-Life-Talent channel. All investments involve risk and the past performance of a security or financial product does not guarantee future results or returns. Work-Life-Talents is not a broker-dealer nor an investment adviser, and makes no representations or warranties, express or implied, and disclaims any and all warranties with respect to any information accessible via any Work-Life-Talents Publications or data.

NO ADVICE OR INFORMATION, WHETHER ORAL OR WRITTEN, OBTAINED FROM THE WORK LIFE TALENT PODCAST OR THROUGH IT'S WEBSITES, PRODUCTS AND SERVICES WILL CREATE ANY WARRANTY NOT EXPRESSLY MADE HEREIN.
</small>

